CannonRV: Measuring radial velocities with a data-driven spectral model

### 2017-01-27 paper/ms2.tex
Add why our RVs are better

@@

%Can you interpret a, b, c in terms of radial velocity? If so, how?
After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate the combined spectra of these stars. These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit. There are two combined spectrums for one star, which are obtained by different method. The radial velocities of the spectrums in Apstar files should be 0, but in fact they are not. This is because of the errors in the radial velocity measurement by the APOGEE team.

@@

@@

\centerline{Fig.1 Comparison of each visit for Star A.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 }

@@

\centerline{Fig.2 Comparison of each visit for Star B.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 }

@@

\centerline{Fig.3 Comparison of each visit for Star C.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 }

@@

\centerline{Fig.4 Comparison of each visit for Star D.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star D is 150. Teff = 4534K Logg =2.24 }

@@

\centerline{Fig.5 Comparison of each visit for Star E.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star E is 177. Teff = 4639K Logg =2.21 }

@@

Finally, we shows our RV shifts results are better than results from the APOGEE team. The evidences are in the following zoom-in plots.

>>>>

In a word, the method we use to calibrate the radial velocities of the combined spectra and individual visits is:

\begin{description}
 \item[1] Infer labels from the fluxes of the combined spectra and individual visits. 
 \item[2] Input these labels into the Cannon and generate inferred fluxes for the combined spectra and individual visits. Use these inferred fluxes as templates to calibrate radial velocities.
 \item[3] Generate optimized fluxes and obtain parameters a, b and c. These parameters show the radial velocity shifts between the data fluxes and the inferred fluxes.
 \item[4] By assuming these inferred fluxes are at rest, derive the radial velocity shifts of these combined spectra and individual visits.
\end{description}

@@

%Can you interpret a, b, c in terms of radial velocity? If so, how?
After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate both the combined spectra and individual visits of these stars. These spectra are stored in Apstar files, which are regenerated onto a common, logarithmically-spaced wavelength scale after removing derived radial velocities of each visit. There are two combined spectrums for one star, which are obtained by different method. The radial velocities of the spectrums in Apstar files should be 0, but in fact they are not. This is because of the errors in the radial velocity measurement by the APOGEE team.

@@

\subsection{\label{sec:level2}Why our method is better}
% In EXP 3

The APOGEE team derive the radial velocities of individual visits by two steps. First, derive the relative radial velocity between each visit and the combined spectrum iteratively. Second, absolute radial velocity determination of the combined spectrum against a grid of synthetic spectra spanning a large range of stellar parameters. All radial velocities in these two steps are determined by cross-correlating a spectrum against a template spectrum. This mean the result is very sensitive to the normalization method since the result of cross-correlation is influenced by normalization prominently. Also, the traditional synthesized spectrum in the second step is not very reliable, which means the absolute velocity is not very accurate. From these two points, there is still much to be improved in APOGEE team's RV results.
\bigskip

In experiment 3, firstly we will show the RVs for individual visits from the APOGEE team is not very reliable. Then, plot our results and compare it with the ones by the APOGEE team. Finally, conclude our method gives a better RV measurement for individual visits.

@@

\centerline{Fig.1 Comparison of each visit for Star A.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 Fe/H =-5.368}

@@

\centerline{Fig.2 Comparison of each visit for Star B.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 Fe/H =3.486}

@@

\centerline{Fig.3 Comparison of each visit for Star C.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 Fe/H =6.577}

@@

\centerline{Fig.4 Comparison of each visit for Star D.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star D is 140. Teff = 5094K Logg =3.088 Fe/H = -3.679 }

@@

\centerline{Fig.5 Comparison of each visit for Star E.}
\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
\centerline{SNR of Star E is 208. Teff = 4869K Logg =1.903 Fe/H = -1.691 }

@@

We will show our results are better than APOGEE's in the nect experiment.

\subsection{\label{sec:level2}Experiment 3}

Finally, we shows our RV shifts results are better than results from the APOGEE team. We demonstrate it by two steps:

\begin{description}
  \item[1] Use inferred fluxes as templates are reliable. These inferred fluxes are at rest.
  \item[2] Our method for deriving the relative radial velocities between inferred fluxes and data spectra is good.

\end{description}

First, we show that use inferred fluxes as templates are reliable. Here we randomly choose 5 stars with different SNR, Teff, logg and Fe/H. Then plot the fluxes from the APOGEE team and the Cannon.

% star 1
\bigskip

\begin{center}
\includegraphics[width=170mm]{Peak_1.png}

\centerline{Fig.16 Comparison of each visit for Star 1.}
\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
\centerline{The black lines show the centers of the peaks in these fluxes}
\centerline{SNR of Star 1 is 206. Teff = 4208K Logg =1.347 Fe/H =-1.018}

% Star 2
\bigskip

\begin{center}
\includegraphics[width=170mm]{Peak_2.png}

\centerline{Fig.17 Comparison of each visit for Star 2.}
\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
\centerline{The black lines show the centers of the peaks in these fluxes}
\centerline{SNR of Star 2 is 197. Teff = 4641K Logg =2.201 Fe/H =-5.873}

% Star 3

\begin{center}
\includegraphics[width=170mm]{Peak_3.png}

\centerline{Fig.18 Comparison of each visit for Star 3.}
\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
\centerline{The black lines show the centers of the peaks in these fluxes}
\centerline{SNR of Star 3 is 117. Teff = 4902K Logg =2.639 Fe/H =-1.863}

% Star 4

\begin{center}
\includegraphics[width=170mm]{Peak_4.png}

\centerline{Fig.19 Comparison of each visit for Star 4.}
\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
\centerline{The black lines show the centers of the peaks in these fluxes}
\centerline{SNR of Star 4 is 122. Teff = 4813K Logg =2.736 Fe/H = -1.832 }

% Star 5

\begin{center}
\includegraphics[width=170mm]{Peak_5.png}

\centerline{Fig.20 Comparison of each visit for Star 5.}
\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
\centerline{The black lines show the centers of the peaks in these fluxes}
\centerline{SNR of Star 5 is 113. Teff = 4513K Logg =2.662 Fe/H = -5.215 }

From these plots, we can see that the peak locations of fluxes from the APOGEE team shift, which should not happen because these fluxes are set at rest by the APOGEE team and there shouldn't be shifts between each fluxes. This means the radial velocities from the APOGEE team have some errors. When we look at the fluxes generated from the Cannon, the peaks from individual visits have the same positions. That's to say, we can use inferred fluxes from the Cannon as templates for calibration.
\bigskip

Then, we argue that our method for deriving the relative radial velocities between inferred fluxes and data spectra is good.
